PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-17 paper/sec-results.tex
tenty->twenty

The size of the EW correction is between four and tenty times larger than the
size of the PDF uncertainty: as previously noted in the other cases, this fact
suggests that, once included in a PDF fit, EW corrections can improve the
accuracy of the PDFs. In comparison to the scale uncertainty, the size of the
EW corrections remains negligible at small values of $p_{\mathrm{T}}^{\ell\bar\ell}$,
roughly $p_{\mathrm{T}}^{\ell\bar\ell}\lesssim\SI{400}{\giga\electronvolt}$, while it
becomes up to four times larger than it in the two bins at the largest value of
$p_{\mathrm{T}}^{\ell\bar\ell}$. In this kinematic region, NLO EW corrections might
therefore become even more relevant than NNLO QCD corrections, and should
therefore be mandatorily included in a fit of PDFs to this data set.
Finally, the Monte Carlo uncertainty is well under control, as it remains
mostly negligible in comparison to the PDF, scale and data uncertainty, and to
the size of the EW correction.

>>>>

The size of the EW correction is between four and twenty times larger than the
size of the PDF uncertainty: as previously noted in the other cases, this fact
suggests that, once included in a PDF fit, EW corrections can improve the
accuracy of the PDFs. In comparison to the scale uncertainty, the size of the
EW corrections remains negligible at small values of $p_{\mathrm{T}}^{\ell\bar\ell}$,
roughly $p_{\mathrm{T}}^{\ell\bar\ell}\lesssim\SI{400}{\giga\electronvolt}$, while it
becomes up to four times larger than it in the two bins at the largest value of
$p_{\mathrm{T}}^{\ell\bar\ell}$. In this kinematic region, NLO EW corrections might
therefore become even more relevant than NNLO QCD corrections, and should
therefore be mandatorily included in a fit of PDFs to this data set.
Finally, the Monte Carlo uncertainty is well under control, as it remains
mostly negligible in comparison to the PDF, scale and data uncertainty, and to
the size of the EW correction.
